---
  title: "Computational Musicology"
author: "Leon Bartelsman"
date: "2019"
output: 
  flexdashboard::flex_dashboard:
  storyboard: true
theme: lumen
---
  
  `r knitr::opts_chunk$set(cache = TRUE)`

```{r, cache = FALSE}
# In order to use these packages, we need to install flexdashboard, plotly, and Cairo.
library(tidyverse)
library(plotly)
library(spotifyr)
library(compmus)

source('spotify.R')
```


### Truck-driver modulations in the Year 2525 [tonal analysis]

```{r}
circshift <- function(v, n) {if (n == 0) v else c(tail(v, n), head(v, -n))}

major_key <- 
  c(6.35, 2.23, 3.48, 2.33, 4.38, 4.09, 2.52, 5.19, 2.39, 3.66, 2.29, 2.88)
minor_key <-
  c(6.33, 2.68, 3.52, 5.38, 2.60, 3.53, 2.54, 4.75, 3.98, 2.69, 3.34, 3.17)
key_templates <-
  tribble(
    ~name    , ~template,
    'Gb:maj', circshift(major_key,  6),
    'Bb:min', circshift(minor_key, 10),
    'Db:maj', circshift(major_key,  1),
    'F:min' , circshift(minor_key,  5),
    'Ab:maj', circshift(major_key,  8),
    'C:min' , circshift(minor_key,  0),
    'Eb:maj', circshift(major_key,  3),
    'G:min' , circshift(minor_key,  7),
    'Bb:maj', circshift(major_key, 10),
    'D:min' , circshift(minor_key,  2),
    'F:maj' , circshift(major_key,  5),
    'A:min' , circshift(minor_key,  9),
    'C:maj' , circshift(major_key,  0),
    'E:min' , circshift(minor_key,  4),
    'G:maj' , circshift(major_key,  7),
    'B:min' , circshift(minor_key, 11),
    'D:maj' , circshift(major_key,  2),
    'F#:min', circshift(minor_key,  6),
    'A:maj' , circshift(major_key,  9),
    'C#:min', circshift(minor_key,  1),
    'E:maj' , circshift(major_key,  4),
    'G#:min', circshift(minor_key,  8),
    'B:maj' , circshift(major_key, 11),
    'D#:min', circshift(minor_key,  3))
twenty_five <- 
  get_tidy_audio_analysis('6A1mh31895sUIYEpOfeqC3') %>% 
  compmus_align(sections, segments) %>% 
  select(sections) %>% unnest(sections) %>% 
  mutate(
    pitches = 
      map(segments, 
          compmus_summarise, pitches, 
          method = 'acentre', norm = 'manhattan')) %>% 
  compmus_match_pitch_template(key_templates, 'aitchison', 'manhattan') %>% 
  ggplot(
    aes(x = start + duration / 2, width = duration, y = name, fill = d)) +
  geom_tile() +
  scale_fill_viridis_c(option = 'E') +
  theme_minimal() +
  labs(x = 'Time (s)', y = '', fill = 'Distance')
ggplotly(twenty_five)
```

***
  
  I had two nice keygrams for ornithology and how high the moon. after trying to put them together on this card i broke everything. For some F reason I am now not able to get them back at all. And now also my  similarity matrices are not what they were before... I am incredibly frustrated now. My apologies for the tone. 
